Indexes measures for oak decline severity using phenotypic descriptors

### 2019-09-12 manuscript/manuscript.Rmd
added abstract and more section headings

# Introduction

# Materials and methods

# Results

## Additional Descriptors

@@

**Estimated crown volume (m<sup>3</sup>)** - estimated volume of crown as an ellipsoid proportional to the crown condition.

@@

***Agrilus* exit hole density (m<sup>-2</sup>)** - density of observed *Agrilus* exit holes across the surveyed trunk area.
$$e = \frac{h}{\frac{2d}{100}\pi}$$
$h$ = number of *Agrilus* exit holes, $d$ = diameter at breast height (cm)

# Discussion

# Conclusions

# References

```{r check}
source('../code/check.R')
check()
```

>>>>

## Abstract

Two indexes, the Phenotypic Decline Index (PDI) and the Decline Acuteness Index (DAI), were developed to describe acute and chronic oak decline severity using a multitude of easily measurable phenotypic descriptors.
Measured phenotypic descriptors include aspects of tree shape and size, crown condition and the presence of biotic agents.
These were collected from 174 trees exhibiting a spectrum of decline severity at 9 sites from across the south, east and west of England.
Inter site differences were identified as a results of aspects of tree size which were corrected for using a mean centring adjustment.
The decline indexes were then calculated using proximity values from an unsupervised random forest of the phenotypic descriptors, multidimensional scaling (MDS) and min-max scaling.
These indexes are simple but sensitive measures of tree decline severity allowing easy comparisons of oak trees both spatially and temporally providing a useful tool for forest monitoring and management.

## Introduction

## Materials and methods

### Phenotypic data collection

### Phenotypic descriptor preparation and analysis

## Results

### Phenotypic descriptors

The following four additional descriptors were calculated:

@@

**Estimated crown volume (m^3^)** - estimated volume of crown as an ellipsoid proportional to the crown condition.

@@

***Agrilus* exit hole density (m^-2^)** - density of observed *Agrilus* exit holes across the surveyed trunk area.
$$e = \frac{h}{\frac{2d}{100}\pi}$$
$h$ = number of *Agrilus* exit holes, $d$ = diameter at breast height (cm)

### Tree size descriptor adjustment by site

### Phenotypic decline and decline acuteness indexes

## Discussion

### Applications

## Conclusions

## References

```{r check,comment=''}
source('../code/check.R')
manuscript_check()
```
